Lossy compression of DNA sequencing quality data

### 2015-07-17 bioinformatics_manuscript/q-compression.tex
renamed previous manuscript directory, created new manuscript directory for BMC, populated it with the BMC LaTeX template directory and moved compression.bib

\author[Hill \textit{et~al.}]{Christopher M. Hill\,$^{1}$, Andr\'{a}s
  Szolek\,$^{2}$, Mohamed El Hadidi\,$^{3}$, and Michael
  P. Cummings\,$^4$\footnote{to whom correspondence should be
    addressed}} \address{$^{1}$Department of Computer Science,
  University of Maryland, College Park, Maryland, 20742
  USA\\ $^{2}$Department of Applied Bioinformatics, Center for
  Bioinformatics, Quantitative Biology Center, and Department of
  Computer Science, University of T\"{u}bingen, Sand 14, 72076
  T\"{u}bingen, Germany\\ $^{3}$Department of Algorithms in
  Bioinformatics, Center for Bioinformatics, University of
  T\"{u}bingen, Sand 14, 72076 T\"{u}bingen, Germany \\ $^{4}$ Center
  for Bioinformatics and Computational Biology, University of
  Maryland, College Park, Maryland, 20742 USA}

@@

\section{Results:}
Lossy compression of quality information can greatly decrease memory
requirements with little or no negative, and our results demonstrate
that some compression methods can result in transformed quality values
that are quite useful, and in some cases advantageous, compared to
original uncompressed values.

>>>>

\author[Hill \textit{et~al.}]{Christopher M. Hill\,$^{1}$, Andr\'{a}s
  Szolek\,$^{2}$, Mohamed El Hadidi\,$^{3}$, and Michael
  P. Cummings\,$^4$\footnote{to whom correspondence should be
    addressed}} \address{$^{1}$Department of Computer Science,
  University of Maryland, College Park, Maryland, 20742
  USA\\ $^{2}$Department of Applied Bioinformatics, Center for
  Bioinformatics, Quantitative Biology Center, and Department of
  Computer Science, University of T\"{u}bingen, Sand 14, 72076
  T\"{u}bingen, Germany\\ $^{3}$Department of Algorithms in
  Bioinformatics, Center for Bioinformatics, University of
  T\"{u}bingen, Sand 14, 72076 T\"{u}bingen, Germany \\ $^{4}$Center
  for Bioinformatics and Computational Biology, University of
  Maryland, College Park, Maryland, 20742 USA}

@@

\section{Results:}
Lossy compression of quality information can greatly decrease memory
requirements, and our results demonstrate
that some compression methods can result in transformed quality values
that are quite useful, and in some cases advantageous, compared to
original uncompressed values.
